\chapter{Chapter 6. Conclusions and Future Work}

We showed that the distributions of a wide variety of parameters generally follow power laws. The magnetic structures identified by the wavelet analysis were also characterized based on MHD quantities ($\sigma_m$, $\sigma_c$, $\sigma_r$). The different criteria assisted us to distinguish different types of events in terms of dynamic and quasi-static structures in the two regions. This work intended to examine the differences in the properties primarily obtained from the GS-based characterization of the identified SFR structures in the solar wind and magnetosheath. The additional findings of this study are summarized as follows.
\begin{enumerate}
    \item The magnitudes of the Wal\'en slope $|w|$ and cross helicity $\sigma_c$ parameters indicate the effect of the remaining plasma flow of the identified structures. Results from both regions indicate that about one-third of structures possess modest (e.g., $|w|>0.3$) remaining flow relative to the total number of structures identified.
    \item SFR structures are generally compressed downstream of the bow shock in the magnetosheath: the scale sizes are smaller while magnetic field strength increases in the magnetosheath. In addition, the magnetic helicity density per unit volume is about one order of magnitude larger than the corresponding value in the solar wind, implying an overall decrease in volume for the SFRs in the magnetosheath.
    \item A significant rotation in the polar angle of the $z$-axis in the magnetosheath is seen when compared to the angle in the solar wind, while the distributions of the azimuthal angle maintain two broad peaks separated by approximately 180 degrees. 
\end{enumerate}