% Type your Acknowledgements below. Delete all the text after the double-spacing command.
\chapter{Acknowledgements}
\doublespacing

% You must pay your scholarly debts by thanking those who have provided intellectual guidance, facilities, or financial support for your project; thus, you thank those who have been significantly involved in your work. You must acknowledge any agency providing funding or other resources, and any individual or institution who has granted you permission to reprint material.

I would like to express my gratitude to my advisor, Qiang Hu. He has guided and supported me along my PhD journey. I would also like to thank my committee members: Drs. Gary Zank, Lingling Zhao, Jakobus le Roux, and Laxman Adhikari, for their effort in helping me successfully complete this work. Further more, I would also like to acknowledge the assistance and encouragement given to me by Yu Chen, who has graciously assisted me with the GS-based reconstruction code.

This work was funded by NASA Grants 80NSSC21K0003, 80NSSC21K1763, 80NSSC21K1319, and NSF Grant AGS‐2229065. I acknowledge NASA contract NAS5-02099 and V. Angelopoulos for use of data from the THEMIS Mission. Specifically: K. H. Glassmeier, U. Auster and W. Baumjohann for the use of FGM data \citep{Auster:2008} provided under the lead of the Technical University of Braunschweig and with financial support through the German Ministry for Economy and Technology and the German Center for Aviation and Space (DLR) under contract 50 OC 0302, and C. W. Carlson and J. P. McFadden for use of ESA \citep{McFadden:2008} data. I thank the individuals who support the MMS mission, specifically that of the FIELDS team \citep{Torbert:2016} and the FPI team \citep{Pollock:2016}, as well as those who make the data readily available. The data used in this study was retrieved from the NASA Science Data Center via the PySPEDAS software, which is open source and publicly available at \url{https://github.com/spedas/pyspedas} under an MIT license. I would like to gratefully acknowledge Wenli Mo and Savvas Raptis for their correspondence providing the MMS data set\footnote{\url{https://zenodo.org/records/11032322}} classified in different magnetospheric regions \citep{ToyEdens:2024}.

% If you wish, you may also thank family or friends. You may conclude your acknowledgments with a dedication rather than using a separate dedication page. Your acknowledgments should be brief and consistent in tone with a formal publication.

I would also like to acknowledge the people who have supported me in my personal (and also professional) endeavors. Words can't even describe how grateful I am for the unwavering support that partner Clayton has given me. I would not be where I am today without his dedication to being there for me. I would also like to say thank you to my friends and co-workers for helping me talk through coding issues, going to conferences together, and just making each day in the office entertaining. \\


\noindent \textit{I would like to dedicate this work to my two best work-from-home buddies, Dorrine and Konrad, who were supposed to be here but life had other plans. To my baby girl Dorrine: thank you for your many, loud suggestions and for also trying to help type some of this document. To Konrad: I wrote the bulk of this while waiting for updates about you, or while visiting you, or while thinking of you. Thanks for all the moral support, baby man.}